The Sloan Digital Sky Survey Spectroscopic Reduction Pipeline

### 2005-03-09 doc/paper/paper2d.tex
Make TeXable.

We select relatively bright F dwarfs as spectrophotometric 
standards.  Ideally, we want the low-metallicity, halo stars in order 
to have spectra that have atmospheric opacities that are easy to model.
The F stars are chosen to satisfy the following color criteria:
$$ 0.6 < u-g < 1.2 $$
$$ 0.0 < g-r < 0.6 $$
$$ g-r > 0.75 * (u-g) - 0.45 $$
as shown in Figure ???.
This selects stars that are on the blue edge of the main
sequence in (u-g) color.  At high Galactic latitudes,
??? stars per square degree fall in this color box.
Targetting priority is given to
those stars with colors closest to the following:
$$ u-g = 0.80 $$
$$ g-r = 0.30 $$
$$ r-i = 0.10 $$
This is meant to select those stars closest in color to BD +17 4708,
which is computed to have a similar color (0.93, 0.28, 0.01, courtesy
of David Hogg, priv. comm.).
From these stars, we select 8 on each plate in the magnitude
range $15.5 < g < 17.0$ (which we call SPECTROPHOTO_STD stars)
and 8 in the magnitude range $17.0 < g < 18.5$ (which we call
REDDEN_STD stars).
These magnitude limits are chosen to avoid nearing saturation
of the CCDs on the bright end, but to still ensure good S/N
on the faint end.
Assuming an absolute magnitude of 4.3 for these stars, this
implies distances of $1.7 < d < 3.5$ kpc for the SPECTROPHOTO_STD
stars and $3.5 < d < 6.9$ kpc for the REDDEN_STD stars.
Note that the color-selection and magnitude cuts are done on
``instrinsic'' magnitudes, meaning that we first apply corrections
for SFD extinction under the assumption that these stars are
completely behind the Galactic dust.

@@

The stuff I'm calibrating to has been public for a while.  The original
ref is Gray & Corbally, 1994, AJ 107, 742.  There are some updates in
Gray, Graham, & Hoyt 2001, AJ, 121, 2159.  Gray's code SPECTRUM is
available http://www.acs.appstate.edu/dept/physics/spectrum/spectrum.html
You can't download the models -- you have to run them.  But I can send you
the ones I've run if you like.  (They start out as text, then I convolve
to SDSS resolution and make FITS files.)  Richard Gray was pretty nice
about resonding to email too.

>>>>

We select relatively bright F dwarfs as spectrophotometric 
standards.  Ideally, we want the low-metallicity, halo stars in order 
to have spectra that have atmospheric opacities that are easy to model.
The F stars are chosen to satisfy the following color criteria:
$$ 0.6 < u-g < 1.2 $$
$$ 0.0 < g-r < 0.6 $$
$$ g-r > 0.75 * (u-g) - 0.45 $$
as shown in Figure ???.
This selects stars that are on the blue edge of the main
sequence in (u-g) color.  At high Galactic latitudes,
??? stars per square degree fall in this color box.
Targetting priority is given to
those stars with colors closest to the following:
$$ u-g = 0.80 $$
$$ g-r = 0.30 $$
$$ r-i = 0.10 $$
This is meant to select those stars closest in color to BD +17 4708,
which is computed to have a similar color (0.93, 0.28, 0.01, courtesy
of David Hogg, priv. comm.).
From these stars, we select 8 on each plate in the magnitude
range $15.5 < g < 17.0$ (which we call SPECTROPHOTO\_STD stars)
and 8 in the magnitude range $17.0 < g < 18.5$ (which we call
REDDEN\_STD stars).
These magnitude limits are chosen to avoid nearing saturation
of the CCDs on the bright end, but to still ensure good S/N
on the faint end.
Assuming an absolute magnitude of 4.3 for these stars, this
implies distances of $1.7 < d < 3.5$ kpc for the SPECTROPHOTO\_STD
stars and $3.5 < d < 6.9$ kpc for the REDDEN\_STD stars.
Note that the color-selection and magnitude cuts are done on
``instrinsic'' magnitudes, meaning that we first apply corrections
for SFD extinction under the assumption that these stars are
completely behind the Galactic dust.

@@

The stuff I'm calibrating to has been public for a while.  The original
ref is Gray \& Corbally, 1994, AJ 107, 742.  There are some updates in
Gray, Graham, \& Hoyt 2001, AJ, 121, 2159.  Gray's code SPECTRUM is
available http://www.acs.appstate.edu/dept/physics/spectrum/spectrum.html
You can't download the models -- you have to run them.  But I can send you
the ones I've run if you like.  (They start out as text, then I convolve
to SDSS resolution and make FITS files.)  Richard Gray was pretty nice
about resonding to email too.
